Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/relatedworks.tex

\section{Related work}
\label{sec:related}
Continuous and near continuous reinforcement learning, which is at the core of
our approach has been thoroughly studied in the deterministic case
in~\cite{adv_upd} or \cite{cont_rl}, but has not been applied in the context of
deep reinforcement learning.

>>>>

%! TEX root = icml_drau.tex
\section{Related work}
\label{sec:related}

Our approach largely builds on \cite{adv_upd}, who identified the
collapse of Q-learning for small time steps and suggested advantage
updating with proper $\deltat$ scalings as a solution.

Continuous and near continuous reinforcement learning, which is at the core of
our approach has been thoroughly studied in the deterministic case
in~\cite{adv_upd} or \cite{cont_rl}, but has not been applied in the context of
deep reinforcement learning.
